---
title: "project"
author: "Jie Chen"
date: "6/4/2020"
output: html_document
---

# SQL projects

## Level 1. Create an AWS datbase to store a personal copy of data in a specific structure

```{r}
library(DBI)
library(RMySQL)

db_user <- 'admin'
db_password <- 'password'
db_name <- 'squirrel'
db_host <- 'squirreldb.co2wkricnwhs.us-east-2.rds.amazonaws.com'
db_port <- 3306

mydb <- dbConnect(MySQL(), user = db_user, password = db_password, dbname = db_name, host = db_host, port = db_port)

summary(mydb)
```
### Upload the Squirrel Data into my SQL database

```{r}

# Load squirrel data
squirrelData <- read.csv("Squirrel_Data.csv")

# List the tables in the DB
dbListTables(mydb)

# Store squirrel data to the DB
dbWriteTable(mydb, 'squirrelData', squirrelData)

#List tables to see that table was added
dbListTables(mydb)

# Read squirrel data table
# dbReadTable(mydb, 'squirrelData')
```

### Create two new tables, one that gives the squirrel sighting characteristics by primary fur color and another by secondary fur color

```{r}
library(dplyr)

# By primary fur color
primary_fur_color <- squirrelData %>%
  select(c(1:7, 9)) %>%
  rename(unique_squirrel_id = Unique.Squirrel.ID, hectare_squirrel_number = Hectare.Squirrel.Number, primary_fur_color = Primary.Fur.Color)

# Delete primaryFurColor table if it exists
dbGetQuery(mydb, "DROP TABLE IF EXISTS primaryFurColor;")

# Store squirrel data to the DB by primary fur color
dbWriteTable(mydb, 'primaryFurColor', primary_fur_color)

# Get primaryFurColor table
dbGetQuery(mydb, "SELECT * FROM primaryFurColor ORDER BY primary_fur_color;")


# By highlight fur color
highlight_fur_color <- squirrelData %>%
  select(c(1:7, 10)) %>%
  rename(unique_squirrel_id = Unique.Squirrel.ID, hectare_squirrel_number = Hectare.Squirrel.Number, highlight_fur_color = Highlight.Fur.Color)

# Delete highlightFurColor table if it exists
dbGetQuery(mydb, "DROP TABLE IF EXISTS highlightFurColor;")

# Store squirrel data to the DB
dbWriteTable(mydb, 'highlightFurColor', highlight_fur_color)

# List the tables in the DB
dbListTables(mydb)

# Get primaryFurColor table
dbGetQuery(mydb, "SELECT * FROM highlightFurColor ORDER BY highlight_fur_color;")

```

## Level 2. Create an AWS database linked to an API

### Get auth

```{r}
#install.packages("jsonlite")
library(jsonlite)
#install.packages("httpuv")
library(httpuv)
#install.packages("httr")
library(httr)
# Can be github, linkedin etc depending on application
oauth_endpoints("github")
# Change based on what you 
myapp <- oauth_app(appname = "SQL-Project-Test",
                   key = "2238a14cb35e0055b35c",
                   secret = "9235537eaa1a43c8208cf4e9bef81eec34558248")
# Get OAuth credentials
github_token <- oauth2.0_token(oauth_endpoints("github"), myapp)
```

### Pull data from Wenyan-Lang, a famous Chinese IDE

```{r}
library(dplyr)

#Add repos you want to pull from
#repos <- c("Sentiment-Analysis-MASC/pulls")
repos <- c("wenyan/forks", "book/forks")

gtoken <- config(token = github_token)

D2 <- data.frame(matrix(vector(), 0, 3))
names(D2) <- c("username","fork.date","unit")
for(i in 1:2){
    
  unit <- paste("https://api.github.com/repos/wenyan-lang/", repos[i], sep = "")
  # Use API
  req <- GET(unit)
  # Take action on http error
  stop_for_status(req)
  
  # Extract content from a request
  json1 = content(req)
  
  # Convert to a data.frame
  gitDF = jsonlite::fromJSON(jsonlite::toJSON(json1))
  
  # Subset data.frame
  #gitDF[gitDF$full_name == "github-api", "created_at"] 
  
  user <- gitDF$owner$login
  pull.date <- gitDF$created_at
  
  if(is.null(user)){
      gitDF <- NULL
      D1 <- NULL   
  } else {
      D1 <- data.frame(unlist(user), unlist(pull.date))
      names(D1) <- c("username","fork.date")
      D1$unit <- repos[i]
      D2 <- bind_rows(D1, D2)
      D2$fork.date <- substr(D2$fork.date, 1,10)
      gitDF <- NULL
      D1 <- NULL
  }
}

```


### Uplaod data into SQL database

```{r}
library(stringr)

# Store pulled data to the DB
dbWriteTable(mydb, 'wenyanlangFork', D2)

# Get dates that have pull data
unique.date <- unique(D2$fork.date)

# Create separate tables that represent each day that data has been pulled from Github  
for(i in 1:length(unique.date)){
  dtdate <- unique.date[i]
  dt <- D2[D2$fork.date == dtdate,]
  dtname <- paste('wenyanlangFork', str_replace_all(dtdate, "-", ""), sep = "")
  # Delete primaryFurColor table if it exists
  dbGetQuery(mydb, paste("DROP TABLE IF EXISTS", dtname, ";"))
  dbWriteTable(mydb, dtname, dt)
}

dbListTables(mydb)
```

## Level 3. Create an RStudio server in the Cloud
